---
title: "Language Learning Platforms"
output:
  html_document:
    df_print: paged
---
### Scenario

Students in a foreign language course choose to use
Duolingo or Anki to help study for the final exam. Compare number
of hours using the app against final exam score across app type.


Read in data

```{r}
languages = read.table("languages.csv", header = TRUE, sep = ",")
duolingo = languages[which(languages$app == "Duolingo"),]
anki = languages[which(languages$app == "Anki"),]
colnames(anki)
colnames(duolingo)
```

Boxplots and two-sample t-test

```{r}
# Load necessary libraries
library(ggplot2)

# Create a more attractive boxplot
ggplot(languages, aes(x = app, y = final, fill = app)) +
  geom_boxplot(outlier.colour = "red", outlier.shape = 16, outlier.size = 2) +
  labs(title = "Final Exam Scores by App Type",
       x = "App Type",
       y = "Final Exam Score") +
  scale_fill_manual(values = c("Duolingo" = "skyblue", "Anki" = "salmon")) +
  theme_minimal() +
  theme(legend.position = "none")

```

T Test

```{r}
t.test(duolingo$final, anki$final, alternative = "two.sided", var.equal = FALSE)
```

Scatterplot

```{r}
colors = c("red", "blue")
plot(languages$hours, languages$final, pch = 19, col = colors[factor(languages$app)], xlab = "Hours Used", ylab = "Final Exam Score")
legend("topleft", legend = c("Anki", "Duolingo"), pch = 19, col = colors)  # Put the legend in the top right corner
abline(lm(final ~ hours, data = duolingo), col = "blue")
abline(lm(final ~ hours, data = anki), col = "red")
```

Final exam score - Test for appropriateness of ANACOVA

```{r}
languages$duolingo = ifelse(languages$app == "Duolingo", 1, 0)
full = lm(final ~ hours + duolingo + hours*duolingo, data = languages)
reduced = lm(final ~ hours + duolingo, data = languages)
anova(full)
anova(reduced)
```

Final exam score - Test for equality of adjusted means

```{r}
full = lm(final ~ hours + duolingo, data = languages)
reduced = lm(final ~ hours, data = languages)
anova(full)
anova(reduced)
```


### Results 

After an inital analysis Duolingo users appear to perform better on avereage on the test, Duolingo users also studied for more hours on average.  This longer time studying could be a results of the more enjoyable gamification of learning that Duolingo implements, and be a testimate to their systems.  Going deeper to discover if Duolingo still outpreforms Anki on an hour basis we conduct a test.  After adjusting the mean scores of both groups (Duoling and Anki), Duolingo users still significantly outpreform Anki Users.  This indicates that on a per hour return basis Duolingo is superior to Anki, and overall the interface and learning curriculum implemented by Duolingo could contribute to users spending more time overall studying.  These 2 effects combined show the superiority of Duolingos platform to learning languages.
